Halo alignments with large scale tidal and velocity fields

### 2013-05-21 paper/main.tex
finished historical review + shape table

@@

TABLA
\begin{table*}
SPIN
\begin{tabular}{cccccc}\hline\hline
Author & Web Method & Spatial Scale & Along &
Alignment & Mass dependence\\\hline

\citep{Faltenbacher2009} %galaxy alignments with mocks

The tidal connection between voids in simulations \citep{Platen2008},
the alignment of observed galaxies with the inferred tidal
field\citep{Lee2007,Jones2010}

@@

\end{tabular}\\
\caption{Summary of previous theoretical results.
Angular Momentum}
\end{table*}

@@

\item
\citep{Paz2008} %angular momentum alignments
Nelson? Puedes hacer un resumen?

@@

The simulation has $512^3$ particles in a cubic box of $150$\hMpc. The
mass per particle is $2\times 10^{9}$\hMsun. 
Halo identitification is done with the HOP algorithm. They keep halos with more
than $50$ partices and less than $5000$, defining a mass range of
$1-100\times 10^{11}$\hMsun.

>>>>

The tidal connection between voids in simulations \citep{Platen2008},
the alignment of observed galaxies with the inferred tidal
field\citep{Lee2007,Jones2010}. There are other kind of alignment
statistics based on modifications of the correlation
\citep{Paz2008,Faltenbacher2009} that go beyond a local computation
and therefore are not reviewed in detail in this paper.

@@

\begin{table*}
\begin{tabular}{cccccc}\hline\hline
Author & Web Method & Spatial Scale & Along &
Alignment & Mass dependence\\\hline

\cite{Libeskind2013} & V-Web & $1 \hMpc$ & 
filament &$++$ & $>10^{12}$\hMsun\\

\cite{Zhang2009}  & Hessian density field &  $2.1$\hMpc & 
filament & $++$ & $>10^{12}\hMsun$\\

& &  & 
filament & $+$ & $<10^{12}\hMsun$\\

& & - &
filament& $++$ & $>10^{12}$\hMsun\\

& & - &
filament& $+$ & $<10^{12}$\hMsun\\\hline \hline

\end{tabular}\\
\caption{Summary of previous theoretical results.
Shape. Indicates the alignment of the halo's major axis along a
filament or a sheet.} 
\end{table*}

\begin{table*}
\begin{tabular}{cccccc}\hline\hline
Author & Web Method & Spatial Scale & Along &
Alignment & Mass dependence\\\hline

@@

\end{tabular}
\caption{Summary of previous theoretical results.
Angular Momentum}
\end{table*}

@@

@@

The simulation has $512^3$ particles in a cubic box of $150$\hMpc. The
mass per particle is $2\times 10^{9}$\hMsun.  Halo identitification is
done with the HOP algorithm. They keep halos with more than $50$
partices and less than $5000$, defining a mass range of$1-100\times
10^{11}$\hMsun.
